Privacy-preserving physical delivery service provisioning using distributed networks

### 2023-01-19 paper/access.tex
refactor proof of fairness

\documentclass{ieeeaccess}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{url}
\usepackage{listings}
\usepackage{pdfpages}
\usepackage[english]{babel}
\usepackage{xcolor,colortbl}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\usepackage{scalerel}

\newcommand\neutral[1][.75]{\mathbin{\ThisStyle{\vcenter{\hbox{%
  \scalebox{#1}{$\SavedStyle\bullet$}}}}}%
}

\newcommand{\plus}{+}
\newcommand{\minus}{-}

\usepackage{textcomp}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
\doi{10.1109/ACCESS.2017.DOI}

\title{Privacy-preserving service provisioning using distributed networks}
\author{\uppercase{Stanis\l{}aw Bara{\'n}ski} \authorrefmark{1},
\uppercase{Julian Szyma{\'n}ski\authorrefmark{1} } 
 }

@@

\markboth{S. Bara{\'n}ski, J. Szyma{\'n}ski : 
Anonymous provision of services via blockchain}
{S. Bara{\'n}ski, J. Szyma{\'n}ski : 
Anonymous provision of services via blockchain}

@@

\titlepgskip=-15pt

\maketitle
\section{Introduction}
Service providers (SPs) like lawyers, laboratories, auditors, or banks, to provide services, require data that is often associated with the user identity.

@@

To achieve these objectives, we use:
\begin{itemize}
    \item Blockchain (aka message board), to achieve fairness, i.e., as a means for proving that certain actions took place at a certain moment without the trusted third party (TTP).
    \item Anonymous payment methods, like cash or privacy-preserving cryptocurrencies, allowing customers to pay for the services anonymously.
    \item Content-addressable decentralised storage network (like IPFS) to anonymously provide results to customers. 
    \item Provable storage network (like Filecoin) to guarantee that the results are available to the customer even in case of the SP deny of service.
    \item Cryptography
    \begin{itemize}
        \item Symmetric encryption, to encrypt and decrypt results published on the public networks.
        \item Public-key cryptography, and Diffie-Helman key exchange (DHKE) to derive shared secrets for symmetric encryption.
        \item Digital signatures, to achieve authentication and non-repudiation of actions. 
    \end{itemize}

@@

%\paragraph{Contributions}
We contribute to the field of fair exchanges by proposing a simple, practical, and anonymous protocol that does not rely on centralized TTP, but uses decentralized blockchain and
distributed content-addressable storage network.

Also, we support physical materials delivery, which was rarely targeted by other researchers or based on strong and unpractical assumptions.

Our protocol simultaneously provides five main properties:

\begin{itemize}
\item Anonymity: the customer stays anonymous to all external observers throughout the transaction.
\item Fairness: at each step of the protocol, both parties are incentivized to act accordingly to the protocol; otherwise, the misbehaving party ends up in a disadvantaged position.
\item Dispute resolution: at each step of the protocol, the customer can start a dispute and win the case if and only if the SP misbehaved.
\item Blockchain-obvious: the customer using our protocol does not need to interact with the blockchain directly; especially, he does not need to obtain funds and pay for the transaction fees, allowing the use of our protocol for non-technical users.
\item TTP-less: 
our protocol does not rely on a trusted third party to conduct transactions fairly. Only in case of a dispute, the centralised justice is involved, which can be instantiated either with courts and polices, or blockchain-based dispute resolution mechanisms as discussed in Section~\ref{sec:justice}.
\item Physical materials: our protocol allows providing not only digital but also physical materials to the service provider.
\end{itemize}

Some authors have proposed blockchain-based fair-exchange systems that could be adapted to service provision; however, to our best knowledge, we are the first to propose a system that satisfies all five properties stated above. Especially anonymity and physical materials delivery were rarely addressed together, and if so, the protocol was based on TTP and impractical assumptions on banking system~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} or did not address the conflict between parties~\cite{altawyLelantosBlockchainBasedAnonymous2017}.

%\paragraph{Organisation}
The remainder of this paper is organized as follows.
In section~\ref{sec:related-works} we review related works. 
Then, in section~\ref{sec:building-blocks} we discuss the concepts of dispute resolution system, self-sorveign identifiers, fairness, message board, anonimity, payment for services, storage network, result availability, anonymity and confidentiality.
Section~\ref{sec:protocol} describes how the protocol works in detail.
Section~\ref{sec:fairness-analysis} provides a fairness analysis of the proposed protocol.
Section~\ref{sec:discussion} discuss possible improvements. 
Finally, section~\ref{sec:conclusion} concludes the paper.

@@

Also, our protocol does not provide its own dispute resolution mechanism as Themis does. However, we assume the existence of an abstract justice which accepts evidences and ., which can be instantiated with either local court or police, or one of the available online dispute resolution services like Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022}, Aragon Court\footnote{https://aragon.org/aragon-court}, or others~\cite{allenGovernanceBlockchainDispute2019}.

@@

\begin{table}
  \newcommand{\YES}{\cellcolor{green!50}Yes}
  \newcommand{\ID}{\cellcolor{green!25}Identity}
  \newcommand{\PSEUDO}{\cellcolor{green!25}Pseudonym}
  \newcommand{\ANON}{\cellcolor{green!50}Anonymity}
  \newcommand{\NO}{\cellcolor{red!50}No}
  \newcommand{\TTP}{\cellcolor{red!50}TTP}
  \newcommand{\BC}{\cellcolor{green!50}Blockchain}
  \caption{Related work comparision}
  \label{tab:comparision}
  \setlength{\tabcolsep}{3pt}
  \begin{tabular}{|p{38pt}|p{32pt}|p{38pt}|p{35pt}|p{37pt}|p{30pt}|}
  \hline
  Protocol & Fair exchange & Anonymity & Dispute resolution & Trust & Physical delivery \\
  \hline
  Bîrjoveanu, 2015~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} & \YES & \YES & \NO & \TTP & \YES \\
  \hline
  Hinarejos et al., 2019~\cite{hinarejosSolutionSecureCertified2019} & \YES & \NO & \NO & \BC & \NO \\
  \hline
  Themis~\cite{mengThemisDecentralizedEscrow2019} & \YES & \NO & \YES & \BC & \NO \\
  \hline
  Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017} & \YES & \PSEUDO & \NO & \BC & \YES \\
  \hline
  This paper & \YES & \YES & \YES & \BC & \YES \\
  \hline

@@

Overly techniques that achieve anonymity on top of non-privacy-preserving blockchains are: Ethereum's Tornado Cash\cite{pertsevTornadoCashPrivacy2019} (via zkSNARK~\cite{grothSizePairingbasedNoninteractive2016} and MiMC~\cite{albrechtMiMCEfficientEncryption2016}), Bitcoin's Wasabi\footnote{https://wasabiwallet.io/} (via CoinJoin \cite{maxwellCoinJoinBitcoinPrivacy2013}).

@@

\item separate address: each transaction derives a new address uniquely associated with the transaction. Such addresses can be derived using Hierarchical Deterministic Wallets (BIP-32)\footnote{https://github.com/bitcoin/bips/blob/master/bip-0032.mediawiki}.
\item memo: the payments are sent to one SP account but contain an extra field named ``memo'' filled with the unique number provided by the SP in $\mathrm{PoD}$. Each payment containing such value in the memo is considered to pay for the transaction. In case of a dispute, revealing both the payment memo and the $\mathrm{PoD}$ proves the connection.
\end{itemize}

@@

\noindent \textbf
{Content Identifier (cid)}\label{content-identifier-cid} is a term coined by IPFS\footnote{https://docs.ipfs.tech/concepts/content-addressing}. However, since our protocol does not depend on
this particular implementation of the storage network, we let the $\mathrm{cid}$ be any other identifier that securely and uniquely points to the content.

@@

\noindent \textbf
{Step 5. Provision of service}\label{step-5-provision-of-service} 
Once the customer has paid for the transaction either in cash or using the anonymous blockchain, the SP can start providing the service.

@@

\noindent \textbf
{Step 9. Download result}\label{step-9-download-result} 
Having the $\mathrm{cid}$, the customer downloads and decrypts the $\mathrm{result}$ using shared key derived from the customer's secret key $\mathrm{sk(C)}$ and the SP's public key $\mathrm{pk(S)}$ using DHKE method. The protocol ends.

@@

\begin{itemize}
  \item{Anonymous payments} — we use the Monero blockchain \cite{noetherRingSignatureConfidential2015}.
  \item{Storage netowork} — we use the Powergate\footnote{https://github.com/textileio/powergate}, which is a wrapper around Filecoin and IPFS.
  \item{Message board} — we use the Ethereum blockchain \cite{woodEthereumSecureDecentralised2014}; concretely, Truffle Ganache\footnote{https://trufflesuite.com/ganache/} and Solidity language.
  \item{Customer and SP} — we create client side web application (webapp) using \texttt{React}\footnote{https://reactjs.org} for creating UI, \texttt{web3.js}\footnote{https://web3js.org} for interaction with Ethereum, and \texttt{crypto-js}\footnote{https://github.com/brix/crypto-js} for encryption. We use \texttt{MetaMask}\footnote{https://metamask.io} browser extension for signing and submiting transactions to Ethereum's node. We use \texttt{monerod}\footnote{https://monerodocs.org/interacting/monerod-reference/} network client and \texttt{monero-wallet-cli}\footnote{https://monerodocs.org/interacting/monero-wallet-cli-reference/} command-line interface for interacting with Monero blockchain.
\end{itemize}

@@

\paragraph{Fariness}
As showed in Section~\ref{sec:steps} and Appendix~\ref{app:fairness}, the protocol is fair. It is achieved by a undeniable hand-shake mechanism in which the SP first publishes $\mathrm{PoD}$ (step 2.) commiting to package delivery and deadlines of the service, and then the customer accepts it by paying for the service or not (step 3.).

@@

Non-repudiation without TTP is achieved by using the blockchain and digital signatures.

\paragraph{Provable Results Availability}
Content addressable networks such as IPFS can not guarantee the availability of the content. However, the Filecoin network, which works as an incentivisation layer on top of IPFS that guarantees the content availability via economic incentivisations~\cite{protocollabsFilecoinDecentralizedStorage2017} can guarantee the availability of the content.

@@

\paragraph{Costs}
Deploying smart contract consumed 1456577 gas.
Proof of delivery consumed 129649 gas.
Proof of provision consumed 149130 gas.
The price of gas at the time of the experiment (03.01.2023) was $0.000000002227 \frac{\mathrm{ETH}}{\mathrm gas}$\footnote{https://etherscan.io/gastracker}, and the price of 1 $\mathrm{ETH}$ was $1261.97 \mathrm{USD}$.
In result, the cost of 
\begin{itemize}
  \item deploying the smart contract was $0.000000002227 \frac{\mathrm{ETH}}{\mathrm gas} \cdot 1456577 \mathrm{gas} \cdot 1261.97 \frac{\mathrm{USD}}{\mathrm{ETH}} = 4.09 \mathrm{USD}$; 
  \item Proof of delivery was $0.000000002227 \mathrm{\frac{ETH}{gas}} \cdot 129649 \mathrm{gas} \cdot 1261.97 \frac{\mathrm{USD}}{\mathrm{ETH}} = 0.29 \mathrm{USD}$; 
  \item Proof of provision was $0.000000002227 \mathrm{\frac{ETH}{gas}} \cdot 149130 \mathrm{gas} \cdot 1261.97 \frac{\mathrm{USD}}{\mathrm{ETH}} = 0.33 \mathrm{USD}$.
\end{itemize}

@@

Centralised justice is the biggest obstacle in achieving a system that complies with Web 3.0 postulates\footnote{https://en.wikipedia.org/wiki/Web3}.

The possible directions for mitigation of such issues are to either (i) replace local justice with Online Dispute Resolution systems like proposed in Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court\footnote{Aragon Court, Decentralized Dispute Resolution Protocol, https://aragon.org/aragon-court, (last visited Jan. 10, 2023)}, LTO Network\footnote{LTO Network, 2019, https://lto.network/, (last visited Jan. 17, 2023)}, and other blockchain dispute resolution platforms~\cite{allenGovernanceBlockchainDispute2019}; or (ii) make it infeasible to provide incorrect results.

@@

The second approach is more futuristic. Suppose that the service we are undertaking is fully computable. Then, it would be possible by employing proofs of correctness of computations~\cite{ben-sassonSNARKsVerifyingProgram2013} to enforce that only correct computations (hence correct services) are accepted. It would require the complete service examination to be computable, which is hard to achieve in settings where physical materials (like blood) are examined. Concretely, the problem canes down to ``How to represent blood digitally?''. If we could represent urine, blood, saliva, or any other physical material in a binary format and let the customer take a sample, discrete it, and send it to the SP by himself, then the whole chain of integrity could be ensured. Therefore, wrong service provision would be infeasible.

\subsection{Provable availability of the
result}\label{cryptographically-provable-availability-of-results}

Currently, the SP has to publish the result into a peer-to-peer content-addressable storage network, e.g., IPFS. The problem is that nothing prevents the SP from publishing the result, receiving the $\mathrm{cid}$, publishing $\mathrm{PoP}$, and immediately after removing the result from the local storage. In case of dispute, the SP can upload the content again, proving its availability. The SP has no motivation to proceed with this kind of misbehaviour other than putting the customer in a disadvantaged position caused by the lost dispute. We see possible prevention of this misbehaviour by the usage of Filecoin—an incentive layer on top of IPFS that guarantees the content availability via economic incentivisations~\cite{protocollabsFilecoinDecentralizedStorage2017}. With the help of Filecoin, the SP would be obligated to create a deal that guarantees the availability of the result until the deadline of the transaction. Moreover, since Filecoin is a blockchain by itself, it could play both roles of message board and storage network.

\subsection{Self-sovereign identities}
Our research in the field showed that some jurisdictions require SPs to associate the diagnosis with the customer personal information. For example, in Poland all laboratories performing medical diagnostic tests, and collecting the material (except tests for HIV) are obligated to the unambiguous identification and verification of the identity of the patient from whom the material was collected~\footnote{Regulation of the Minister of Health of March 23, 2006 on quality standards for medical diagnostic and microbiological laboratories, https://isap.sejm.gov.pl/isap.nsf/DocDetails.xsp?id=WDU20060610435}.

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{stanislaw.jpg}}]{Stanis\l{}aw Bara{\'n}ski} received BEng in 2019 and MSc in 2020 in informatics at Gdańsk University of Technology. 
Currently, he is a PhD candidate at the Department of Computer Architecture, Faculty of Electronics, Telecommunications and Informatics, Gdansk University of Technology.

His research interests include blockchains and cryptography, especially the issue of blockchain-based internet voting and mitigation of content poisoning attacks via blockchain.

He likes to develop his ideas right up to the commercialization stage. He is the author of multiple mobile and web applications that have reached success on the market. His blockchain-based internet voting project has been funded by the Stellar Community Fund for the most useful Stellar application. 
\end{IEEEbiography}

@@

\section{Appendix A: Proof of fairness}\label{app:proof-of-fairness}
Below we describe each step and rationale of the outcome position.
We use the notation intoruced in Section~\ref{sec:fairness-model} to analise each position in the protocol.

\noindent \textbf
{Step 1. Customer turn: package delivery}\label{step-1-deliver-package}

The customer has delivered the package:

\begin{itemize}
\item Agreeable path:
  \begin{itemize}
  \item
    \(\operatorname{\sigma_{1, c, n} = \neutral}\), the customer has risked its materials but has not paid for the transaction, so we assume he is in the neutral position \footnote{One would argue that the customer has put effort into delivering the materials to the SP or that the sample is valuable. We assume that the sample without personal information is useless, and the effort to deliver the package is negligible.}.
  \item
    \(\operatorname{\sigma_{1, s, n} = \neutral}\), the SP is in a neutral position as she did not put any effort, and the package has not brought any value to the SP.
  \end{itemize}
\item
  Starting a dispute:

  \item
    \(\operatorname{\sigma_{1, c, d} = -}\), the customer loses the case as the SP has still an opportunity to publish proof of provision within the timeframe.
  \item
    \(\operatorname{\sigma_{1, s, d} = \neutral}\), the SP win the case for the same reason.
  \end{itemize}
\end{itemize}

\item
  The customer can follow the protocol to the non-disadvantaged position \(\operatorname{\sigma_{1, c, n} = \neutral}\).
\item
  The SP can do nothing and always ends up in the non-disadvantaged position.
\end{itemize}

\noindent \textbf
{Step 2. SP turn: proof of delivery}\label{step-2-proof-of-delivery}

The SP has published proof of delivery:

>>>>

\documentclass{ieeeaccess}

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}

\usepackage{caption}
\usepackage{url}
\usepackage{listings}
\usepackage{pdfpages}
\usepackage[english]{babel}
\usepackage{xcolor,colortbl}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\usepackage{scalerel}

\newcommand{\plus}{+}
\newcommand{\minus}{-}
\newcommand\neutral[1][.75]{\mathbin{\ThisStyle{\vcenter{\hbox{%
  \scalebox{#1}{$\SavedStyle\bullet$}}}}}%
}

\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\ceil}[1]{\left\lceil #1 \right\rceil}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
\doi{10.1109/ACCESS.2022.0122113}

\title{Privacy-preserving physical delivery service provisioning using distributed networks}
\author{\uppercase{Stanis\l{}aw Bara{\'n}ski} \authorrefmark{1},
\uppercase{Julian Szyma{\'n}ski\authorrefmark{1} } 
 }

@@

\markboth{S. Bara{\'n}ski, J. Szyma{\'n}ski : 
Privacy-preserving physical delivery service provisioning using distributed networks}
{S. Bara{\'n}ski, J. Szyma{\'n}ski : 
Privacy-preserving physical delivery service provisioning using distributed networks}

@@

\titlepgskip=-21pt

\maketitle

\section{Introduction}
\label{sec:introduction}
Service providers (SPs) like lawyers, laboratories, auditors, or banks, to provide services, require data that is often associated with the user identity.

@@

To achieve these objectives, we use:
\begin{itemize}
    \item Blockchain (aka message board), to achieve fairness, i.e., as a means for proving that certain actions took place at a certain moment without the trusted third party (TTP).
    \item Anonymous payment methods, like cash or privacy-preserving cryptocurrencies, allowing customers to pay for the services anonymously.
    \item Content-addressable decentralised storage network (e.g., IPFS) to anonymously provide results to customers together with provable storage netwrok (e.g., Filecoin) to guarantee that the results are available to the customer even in case of the SP deny of service. 
    \item Cryptography
    \begin{itemize}
        \item Symmetric encryption, to encrypt and decrypt results published on the public networks.
        \item Public-key cryptography, and Diffie-Helman key exchange (DHKE) to derive shared secrets for symmetric encryption.
        \item Digital signatures, to achieve authentication and non-repudiation of actions. 
    \end{itemize}

@@

%\paragraph{Contributions}
We contribute to the state of the art by:

\begin{itemize}
\item proposing a novel protocol that:
  \begin{itemize}
  \item allows \textbf{anonymous} service provision, i.e., the service provider does not need to collect any personal information from the customer.
  \item achieves \textbf{fairness} by carefully designing the protocol as an interactive non-cooperative game, in which the SP remains in advantageous position, and customer in disadvantageus with the option to start a dispute in case the SP misbehaviour.
  \item \textbf{does not rely on centralized TTP}, but uses decentralized blockchain and distributed content-addressable storage network.
  \item abstracts the customers from the blockchain technology used underneath, allowing the use of our protocol for \textbf{non-technical users}.
  \item allows the \textbf{delivery of physical materials}, which was rarely addressed by other researchers or based on strong and unpractical assumptions.
  \item guarantees the \textbf{remote availability of the results}, even in case of the SP denial of service.
  \end{itemize} 
\item Systemise often misused definitions of anonymity, pseudonymity, linkability, and traceability.
\item Proposing a framework for analysing fairness analysis in fair-exchange protocols.
\item Discuss the possible improvements to the protocol witht the use of secure computation, self-sovereign identities, zero-knowledge proofs, and blockchain-based dispute resolution mechanisms.
\end{itemize}

% Our protocol simultaneously provides five main properties:

% \begin{itemize}
% \item Anonymity: the customer stays anonymous to all external observers throughout the transaction.
% \item Fairness: at each step of the protocol, both parties are incentivized to act accordingly to the protocol; otherwise, the misbehaving party ends up in a disadvantaged position.
% \item Dispute resolution: at each step of the protocol, the customer can start a dispute and win the case if and only if the SP misbehaved.
% \item Blockchain-obvious: the customer using our protocol does not need to interact with the blockchain directly; especially, he does not need to obtain funds and pay for the transaction fees, allowing the use of our protocol for non-technical users.
% \item TTP-less: 
% our protocol does not rely on a trusted third party to conduct transactions fairly. Only in case of a dispute, the centralised justice is involved, which can be instantiated either with courts and polices, or blockchain-based dispute resolution mechanisms as discussed in Section~\ref{sec:decentralised-justice}.
% \item Physical materials: our protocol allows providing not only digital but also physical materials to the service provider.
% \end{itemize}

Some authors have proposed blockchain-based fair-exchange systems that could be adapted to service provision; however, to our best knowledge, we are the first to propose a system that satisfies all the properties stated above. Especially anonymity and physical materials delivery were rarely addressed together, and if so, the protocol was based on TTP and impractical assumptions on banking system~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} or did not address the conflict between parties~\cite{altawyLelantosBlockchainBasedAnonymous2017}.

%\paragraph{Organisation}
The remainder of this paper is organized as follows.
In section~\ref{sec:related-works} we review related works. 
Then, in section~\ref{sec:building-blocks} we discuss the building blocks of dispute resolution system, blockchain as a message board, fairness, payment for services, storage network, result availability, anonymity and confidentiality.
Section~\ref{sec:protocol} describes how the protocol works in detail.
Section~\ref{sec:fairness-analysis} provides a fairness analysis of the proposed protocol.
In Section~\ref{sec:experiments} we present the implementation of the protocol and results of our experiments.
Section~\ref{sec:discussion} discuss possible improvements in terms of crowd sourced dispute resolution or dispute avoidance, self-sovereign identities (SSI), and anonymous delivery.
Finally, section~\ref{sec:conclusion} concludes the paper.

@@

Also, our protocol does not provide its own dispute resolution mechanism as Themis does. However, we assume the existence of an abstract justice that accepts evidence and punishes the misbehaving party. It can be instantiated with either local court or police, or one of the blockchain
dispute resolution services like Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court\footnote{Aragon Court, Decentralized Dispute Resolution Protocol, https://aragon.org/aragon-court, (last visited Jan. 10, 2023)}, LTO Network\footnote{LTO Network, 2019, https://lto.network/, (last visited Jan. 17, 2023)}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}.

@@

\begin{table}
  \newcommand{\YES}{\cellcolor{green!50}Yes}
  \newcommand{\ID}{\cellcolor{green!25}Identity}
  \newcommand{\PSEUDO}{\cellcolor{green!25}Pseudonym}
  \newcommand{\ANON}{\cellcolor{green!50}Anonymity}
  \newcommand{\NO}{\cellcolor{red!50}No}
  \newcommand{\TTP}{\cellcolor{red!50}TTP}
  \newcommand{\BC}{\cellcolor{green!50}BC}
  \caption{Related work comparision}
  \label{tab:comparision}
  \setlength{\tabcolsep}{3pt}
  \begin{tabular}{|p{40pt}|p{35pt}|p{40pt}|p{35pt}|p{30pt}|p{30pt}|}
  \hline
  Protocol & Fair exchange & Anonymity & Dispute resolution & Trust & Physical delivery \\
  \hline
  Bîrjoveanu, 2015~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} & \YES & \YES & \NO & \TTP & \YES \\
  \hline
  Hinarejos et al., 2019~\cite{hinarejosSolutionSecureCertified2019} & \YES & \NO & \NO & \BC & \NO \\
  \hline
  Themis~\cite{mengThemisDecentralizedEscrow2019} & \YES & \NO & \YES & \BC & \NO \\
  \hline
  Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017} & \YES & \PSEUDO & \NO & \BC & \YES \\
  \hline
  This paper & \YES & \YES & \YES & \BC & \YES \\
  \hline

@@

Overly techniques that achieve anonymity on top of non-privacy-preserving blockchains are: Ethereum's Tornado Cash\cite{pertsevTornadoCashPrivacy2019} (via zkSNARK~\cite{grothSizePairingbasedNoninteractive2016} and MiMC~\cite{albrechtMiMCEfficientEncryption2016}), Bitcoin's Wasabi\footnote{Wasabi Wallet, Open-source, non-custodial Bitcoin Wallet for desktop, \url{https://wasabiwallet.io/}, (last visited Nov. 28, 2022)} (via CoinJoin \cite{maxwellCoinJoinBitcoinPrivacy2013}).

@@

\item separate address: each transaction derives a new address uniquely associated with the transaction. Such addresses can be derived using Hierarchical Deterministic Wallets (BIP-32)\footnote{Bitcoin Improvement Proposals,Hierarchical Deterministic Wallets, \url{https://github.com/bitcoin/bips/blob/master/bip-0032.mediawiki}, (last visited Dec. 03, 2022)}.
\item memo: the payments are sent to one SP account but contain an extra field named ``memo'' filled with the unique number provided by the SP in $\mathrm{PoD}$. Each payment containing such value in the memo is considered to pay for the transaction. In case of a dispute, revealing both the payment memo and the $\mathrm{PoD}$ proves the connection.
\end{itemize}

@@

\noindent \textbf
{Content Identifier (cid)}\label{content-identifier-cid} is a term coined by IPFS\footnote{IPFS, Content addressing and CIDs, \url{https://docs.ipfs.tech/concepts/content-addressing}, (last visited Dec. 01, 2022)}. However, since our protocol does not depend on this particular implementation of the storage network, we let the $\mathrm{cid}$ be any other identifier that securely and uniquely points to the content.

@@

\noindent \textbf
{Step 5. Provision of service}\label{step-5-provision-of-service}

Once the customer has paid for the transaction either in cash or using the anonymous blockchain, the SP can start providing the service.

@@

\noindent \textbf
{Step 9. Download result}\label{step-9-download-result}

Having the $\mathrm{cid}$, the customer downloads and decrypts the $\mathrm{result}$ using shared key derived from the customer's secret key $\mathrm{sk(C)}$ and the SP's public key $\mathrm{pk(S)}$ using DHKE method. The protocol ends.

@@

\begin{itemize}
  \item{Anonymous payments} — we use the Monero blockchain \cite{noetherRingSignatureConfidential2015}.
  \item{Storage netowork} — we use the Powergate\footnote{Powergate, \url{https://github.com/textileio/powergate}, (last visited Dec. 20, 2022)}, which is a wrapper around Filecoin and IPFS.
  \item{Message board} — we use the Ethereum blockchain \cite{woodEthereumSecureDecentralised2014}; concretely, Truffle Ganache\footnote{Truffle Ganache, \url{https://trufflesuite.com/ganache/}, (last visited Dec. 20, 2022)} and Solidity language.
  \item{Customer and SP} — we create client side web application (webapp) using \texttt{React}\footnote{React, A JavaScript library for building user interfaces, \url{https://reactjs.org}, (last visited Dec. 20, 2022)} for creating UI, and \texttt{web3.js}\footnote{web3.js, A JavaScript library for building on Ethereum, \url{https://web3js.org}, (last visited Dec. 20, 2022)} for interaction with Ethereum. We use \texttt{MetaMask}\footnote{MetaMask, A crypto wallet \& gateway to blockchain apps, \url{https://metamask.io}, (last visited Dec. 20, 2022)} browser extension for signing and submiting transactions to Ethereum's node. We use \texttt{monerod}\footnote{Monero, The Monero daemon \texttt{monerod}, \url{https://monerodocs.org/interacting/monerod-reference/}, (last visited Dec. 20, 2022)} network client and \texttt{monero-wallet-cli}\footnote{Monero, The CLI client for Monero, \url{https://monerodocs.org/interacting/monero-wallet-cli-reference/}, (last visited Dec. 20, 2022)} command-line interface for interacting with Monero blockchain.
\end{itemize}

@@

\paragraph{Fariness}
As showed in Section~\ref{sec:steps} and Appendix~\ref{app:proof-of-fairness}, the protocol is fair. It is achieved by a undeniable hand-shake mechanism in which the SP first publishes $\mathrm{PoD}$ (step 2.) commiting to package delivery and deadlines of the service, and then the customer accepts it by paying for the service or not (step 3.).

@@

Non-repudiation without TTP is achieved by using the blockchain and digital signatures. Blockchain guarantees that each change to the state of the smart contract is visible to everyone and only the SP is allowed to modify its state.

\paragraph{Provable Results Availability}
Content addressable networks such as IPFS can not guarantee the availability of the content\footnote{Nothing prevents the SP from publishing the result, receiving the $\mathrm{cid}$, publishing $\mathrm{PoP}$, and immediately after removing the result from the local storage. In case of dispute, the SP can upload the content again, proving its availability. The SP has no motivation to proceed with this kind of misbehaviour other than putting the customer in a disadvantaged position caused by the lost dispute.}. However, the Filecoin network, which works as an incentivisation layer on top of IPFS, increases the content availability via economic incentivisations (i.e., punishment in case of lack of proof of storage of the content)~\cite{protocollabsFilecoinDecentralizedStorage2017}.

@@

\paragraph{Costs}
Deploying smart contract consumed 1456577 gas.
Proof of delivery consumed 129649 gas.
Proof of provision consumed 149130 gas.
The price of gas at the time of the experiment (Jan. 03, 2023) was $0.000000002227 \frac{\mathrm{ETH}}{\mathrm gas}$\footnote{Etherscan, Ethereum Gas Tracker, \url{https://etherscan.io/gastracker}, (last visited Jan. 03, 2023)}, and the price of 1 $\mathrm{ETH}$ was $1261.97 \mathrm{USD}$.
In result, the cost of 
\begin{itemize}
  \item deploying the smart contract was $0.000000002227 \frac{\mathrm{ETH}}{\mathrm gas} \cdot 1456577 \mathrm{gas} \cdot 1261.97 \frac{\mathrm{USD}}{\mathrm{ETH}} = 4.09 \mathrm{USD}$; 
  \item Proof of delivery was $0.000000002227 \mathrm{\frac{ETH}{gas}} \cdot 129649 \mathrm{gas} \cdot 1261.97 \frac{\mathrm{USD}}{\mathrm{ETH}} = 0.29 \mathrm{USD}$; 
  \item Proof of provision was $0.000000002227 \mathrm{\frac{ETH}{gas}} \cdot 149130 \mathrm{gas} \cdot 1261.97 \frac{\mathrm{USD}}{\mathrm{ETH}} = 0.33 \mathrm{USD}$.
\end{itemize}

@@

Centralised justice is the biggest obstacle in achieving a system that complies with Web 3.0 postulates\footnote{Web3, \url{https://en.wikipedia.org/wiki/Web3}, (last visited Jan. 05, 2023)}.

The possible directions for mitigation of such issues are to either (i) replace local justice with blockchain dispute resolution systems like proposed in Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court\footnote{Aragon Court, Decentralized Dispute Resolution Protocol, https://aragon.org/aragon-court, (last visited Jan. 10, 2023)}, LTO Network\footnote{LTO Network, 2019, https://lto.network/, (last visited Jan. 17, 2023)}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}; or (ii) make it infeasible to provide incorrect results.

@@

The second approach is more futuristic. Suppose that the service we are undertaking is fully computable. Then, it would be possible by employing proofs of correctness of computations~\cite{ben-sassonSNARKsVerifyingProgram2013} to enforce that only correct computations (hence correct services) are accepted. It would require the complete service examination to be computable, which is hard to achieve in settings where physical materials (like blood) are examined. Concretely, the problem canes down to ``How to represent blood digitally?''. If we could represent urine, blood, saliva, or any other physical material in a binary format and let the customer take a sample, discrete it, and send it to the SP, then the whole chain of integrity could be ensured. Therefore, incorrect service provision would be infeasible, and hence, disputes would be avoided.

\subsection{Self-sovereign identities}
Our research in the field showed that some jurisdictions require SPs to associate the diagnosis with the customer personal information. For example, in Poland all laboratories performing medical diagnostic tests, and collecting the material (except tests for HIV) are obligated to the unambiguous identification and verification of the identity of the patient from whom the material was collected~\footnote{Regulation of the Minister of Health of March 23, 2006 on quality standards for medical diagnostic and microbiological laboratories, \url{https://isap.sejm.gov.pl/isap.nsf/DocDetails.xsp?id=WDU20060610435}}.

@@

@@

\section{Proof of fairness}\label{app:proof-of-fairness}
Below we describe each step and rationale of the outcome position.
We use the notation introduced in Section~\ref{sec:fairness-model} to analise each position in the protocol and fariness Definition~\ref{def:fairness} to show the fairness of the protocol.

\newcommand{\customer}{customer}
\renewcommand{\sp}{SP}
\newcommand{\AgreeablePath}{Agreeable path:}
\newcommand{\DisputePath}{The customer starts a dispute:}
\newcommand{\Fairness}{Fairness:}
\newcommand{\CustomerTurn}[0]{\expandafter\MakeUppercase customer turn:}
\newcommand{\SPTurn}[0]{\sp{} turn:}

\newcommand{\CanFollowToOne}[2]{The #1 can follow the protocol to the non-disadvantaged position #2}
\newcommand{\CanDoNothing}[1]{The #1 can do nothing and always end up in the non-disadvantaged position}
\newcommand{\CanDoAnything}[1]{The #1 can do anything and always end up in the non-disadvantaged position}
\newcommand{\Pos}[4]{$\operatorname{\sigma_{#1, #2, #3} = #4}$}
\newcommand{\WinForTheSameReason}[1]{The #1 wins the dispute for the same reason}

\newcommand{\CustomerLosesBeforePayment}{The customer loses the dispute because the SP is not obligated to do anything until the transaction is paid}
\newcommand{\CustomerLosesBeforePoP}{The customer loses the dispute because the SP still can publish the PoP within the agreed timeframe}

\newcommand{\normal}{n}
\newcommand{\dispute}{d}
\newcommand{\abnormal}{\overline{n}}
\newcommand{\abdispute}{\overline{d}}
